MPI3

### 2018-04-23 MiP3.Rmd
Finished, maybe?

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE) # Something about loading stuff more quickly

setwd("~/Dropbox/PhD_data/MiP")
library(tidyverse) # For data manipulation and visualization
library(stargazer) # For output tables 
library(plm) # For linear panel regression
library(car) # For logging the dependent variable; might be in tidyverse already 
library(gridExtra) # For multi-plot outputs 
library(maps) # Map data. May also be in tidyverse? 
library(mapdata) # More map data? 
library(R.utils) # capitalizing? 
library(MASS) # Boxcox? May also be in tidyverse? 
```

```{r Data import, include=F}
#### Data ####
# Data from Michael Barber's work on political polarization: 
# https://doi.org/10.1086/683453
Barber <- read_csv("~/Dropbox/PhD_data/MiP/data/Barber/Barber Limits Data.csv")
# Getting 2008 only data (reasons for which will become clear in the next sections)
Barber2008 <- Barber %>% filter(year==2008)

# Data from ICC greasethewheels.org/cci/
# Downloaded as .csv, imported as is. 
convictions <- read_csv("~/Dropbox/PhD_data/MiP/data/ICS/CCI19762015.csv")
perceptions <- read_csv("~/Dropbox/PhD_data/MiP/data/ICS/CPS20142016.csv")
#Doesn't havetime series data 
reflections <- read_csv("~/Dropbox/PhD_data/MiP/data/ICS/CRI19772013.csv")
# Though I don't like the name reflections--it implies an unproven causal relationship.

@@

```{r govtrustgrid, include=F}
govtrustgrid
```

@@

>>>>

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE) # Something about loading stuff more quickly 
library(tidyverse) # For data manipulation and visualization
library(stargazer) # For output tables 
library(plm) # For linear panel regression
library(car) # For logging the dependent variable; might be in tidyverse already 
library(gridExtra) # For multi-plot outputs 
library(maps) # Map data. May also be in tidyverse? 
library(mapdata) # More map data? 
library(R.utils) # capitalizing? 
library(MASS) # Boxcox? May also be in tidyverse? 
theme_set(theme_minimal()) # Sets default theme, I think  
```

```{r Data import, include=F}
#### Data ####
# Data from Michael Barber's work on political polarization: 
# https://doi.org/10.1086/683453
Barber <- read_csv("~/Documents/GitHub/Money-in-Politics/data/Barber/Barber_Limits_Data.csv")
# Getting 2008 only data (reasons for which will become clear in the next sections)
# They didn't get clearer. 
# Barber2008 <- Barber %>% filter(year==2008)

# Data from ICC greasethewheels.org/cci/
# Downloaded as .csv, imported as is. 
convictions <- read_csv("~/Documents/GitHub/Money-in-Politics/data/ICS/CCI19762015.csv")
perceptions <- read_csv("~/Documents/GitHub/Money-in-Politics/data/ICS/CPS20142016.csv")
#Doesn't havetime series data 
reflections <- read_csv("~/Documents/GitHub/Money-in-Politics/data/ICS/CRI19772013.csv")
# Though I don't like the name reflections--it implies an unproven causal relationship.

@@

```{r govtrustgrid, include=F}
# What's this? Leftover from preivous plots, maybe 
# govtrustgrid
```

@@

```{r plots and charts for poster, hopefully}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5, CRIreg1, CRIreg2, CRIreg3, CRIreg5,
  type="text", 
  out="CCICRI.htm",
  dep.var.labels = c("Corruption Convictions Index", "Corruption Reflections Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)",
  notes = "I make this look good!")
          )

ind_limits_2010.histo <- ggplot() + geom_histogram(data=Barber, aes(ind_limits_2010), fill="#bf5700", binwidth = 5000) + theme_minimal() + labs(x = "Individual dollar limits", y= "Count of state-years")
ind2pty_limits_2010.histo <- ggplot() + geom_histogram(data=Barber, aes(ind2pty_limits_2010), fill="#bf5700", binwidth = 5000) + theme_minimal() + labs(x = "Individual-to-party dollar limits", y="")
pac_limits_2010.histo <- ggplot() + geom_histogram(data=Barber, aes(pac_limits_2010), fill="#bf5700", binwidth = 5000) + theme_minimal() + labs(x = "PAC dollar limits", y="")

Barber.histos <- grid.arrange(ind_limits_2010.histo, ind2pty_limits_2010.histo, pac_limits_2010.histo, nrow=1, bottom="Data from 1990-2012; 99999 indicates no limit", top="How Common Are Different Levels of State-Level Campaign Finance Limits?")

CCI1<-ggplot() + geom_point(data=subset(BarberICC, ind_limits_2010 != 99999), aes(ind_limits_2010,CCI), col="#bf5700")  + labs(x = "Individual dollar limits", y= "Corruption Convictions Index")
CCI2<-ggplot(data=subset(BarberICC, ind2pty_limits_2010 != 99999), aes(ind2pty_limits_2010,CCI)) + geom_point(col="#bf5700") + labs(x = "Individual-to-party dollar limits", y="")
CCI3<-ggplot(data=subset(BarberICC, pac_limits_2010 != 99999), aes(pac_limits_2010,CCI)) + geom_point(col="#bf5700") + labs(x = "PAC dollar limits", y="")

CRI1<-ggplot(data=subset(BarberICC, ind_limits_2010 != 99999), aes(ind_limits_2010,CRI)) + geom_point(col="#bf5700") + labs(x = "Individual dollar limits", y= "Corruption Reflections Index")
CRI2<-ggplot(data=subset(BarberICC, ind2pty_limits_2010 != 99999), aes(ind2pty_limits_2010,CRI)) + geom_point(col="#bf5700") + labs(x = "Individual-to-party dollar limits", y="")
CRI3<-ggplot(data=subset(BarberICC, pac_limits_2010 != 99999), aes(pac_limits_2010,CRI)) + geom_point(col="#bf5700") + labs(x = "PAC dollar limits", y="")
CCIandCRI <- grid.arrange(CCI1, CCI2, CCI3, CRI1,CRI2,CRI3, nrow=2)

# All together now 
grid.arrange(ind_limits_2010.histo, ind2pty_limits_2010.histo, pac_limits_2010.histo, CCI1, CCI2, CCI3, CRI1,CRI2,CRI3, nrow=3)
```

grid.arrange(ind_limits_2010.histo, ind2pty_limits_2010.histo, pac_limits_2010.histo, CCI1, CCI2, CCI3, CRI1,CRI2,CRI3, nrow=3, bottom="Data from 1990-2012; in the top three graphs, 99999 indicates a state-year with no limit in that category")
